---
title: "Fyza's Website for Biostat776"
knit: (function(input_file, encoding) {
  out_dir <- 'docs';
  rmarkdown::render(input_file,
 encoding=encoding,
 output_file=file.path(dirname(input_file), out_dir, 'index.html'))})
author: "Fyza Shaikh"
date: "9/8/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Introduction

Hi, I'm an instructor in the Department of Oncology. My research interests include microbiome and cancer immunotherapy. I completed my MD/PhD at Vanderbilt University in Nashville, moved to Pittsburgh for residency training in Internal Medicine, and then came to Baltimore for fellowship training in Medical Oncology.



Five Fun Facts!

1. I've performed in two water ballets with Fluid Movement as part of a community art group in Baltimore. (This is a synchronized swimming show at public pools in the city during the summer)
2. I am NOT a strong swimmer. 
3. My cat is named Turby because he was so turbulent as a kitten
4. I recently learned to make Szechuan food
5. I used to knit/crochet amigurumi (3D figures)


Interesting links:

I aspire to make beautiful graphs like those here:
https://www.r-graph-gallery.com/index.html


```{r cars}

```



```{r pressure, echo=FALSE}

```


